SSRP Report based on *Who Do Voter ID Laws Keep from Voting?* by Fraga and Miller (2022)

### 2024-02-11 other/ssrp_report/ssrp_report.qmd
Completed the SSRP Report

```{r}
#### Loading Packages ####

# install.packages("tidyverse")
# install.packages("patchwork")
library(tidyverse)
library(patchwork)
```

```{r}
# Loading the cleaned data
reasons_data_cleaned <- read_csv("data/replication/reasons_data_cleaned.csv")
```

@@

Using the R programming language () and the tidyverse (), patchwork (), haven (), and labelled () packages, three figures from *Who Do Voter ID Laws Keep from Voting?* by Fraga and Miller (2022) were reproduced.

```{r}
#| label: fig-2
#| fig-cap: "Reproduction of Figure 2 from Fraga and Miller (2022)"

@@

# Creating the replicated graph
figure_2_replication <-
  ggplot(mapping = aes(x = reorder(figure_2_data$reason, figure_2_data$percent,
                                   decreasing = TRUE),
                       y = figure_2_data$percent)) +
  geom_col() +
  theme_classic() +
  labs(x = "Impediment to voter ID", y = "Percentage",
       title = "Figure 2. Impediments cited by Texas voters in 2016") +
  coord_flip() +
  # The geom_text function used to add the labels to the graph was obtained from
  # R Graphics Cookbook:
  # https://r-graphics.org/recipe-bar-graph-labels
  # The hjust argument used to align the labels was obtained from
  # Cédric Scherer's website:
  # https://www.cedricscherer.com/2021/07/05/a-quick-how-to-on-labelling-bar-graphs-in-ggplot2/
  geom_text(aes(label = figure_2_data$label),
            hjust = c(1, 1, 1, 1, 1, 1, 1, 1),
            colour = "orange") +
  # The expand_limits function used to change the upper limit of the percent
  # axis's scale was obtained from the tidyverse ggplot2 website:
  # https://ggplot2.tidyverse.org/reference/expand_limits.html
  expand_limits(y = 40)

@@

```{r}
#| label: fig-3
#| fig-cap: "Reproduction of Figure 3 from Fraga and Miller (2022)"

@@

# Creating the replicated graph
figure_3_replication <-
  ggplot(mapping = aes(x = reorder(figure_3_data$reason, figure_3_data$percent,
                                   decreasing = TRUE),
                       y = figure_3_data$percent)) +
  geom_col() +
  theme_classic() +
  labs(x = "Impediment to voter ID", y = "Percentage",
       title = "Figure 3. Binned impediments cited") +
  coord_flip() +
  # The geom_text function used to add the labels to the graph was obtained from
  # R Graphics Cookbook:
  # https://r-graphics.org/recipe-bar-graph-labels
  # The hjust argument used to align the labels was obtained from
  # Cédric Scherer's website:
  # https://www.cedricscherer.com/2021/07/05/a-quick-how-to-on-labelling-bar-graphs-in-ggplot2/
  geom_text(aes(label = figure_3_data$label),
            hjust = c(1, 1, 1),
            colour = "orange") +
  # The expand_limits function used to change the upper limit of the percent
  # axis's scale was obtained from the tidyverse ggplot2 website:
  # https://ggplot2.tidyverse.org/reference/expand_limits.html
  expand_limits(y = 40)

@@

```{r}
#| label: fig-a2
#| fig-cap: "Reproduction of Figure A2 from Fraga and Miller (2022)"

@@

# Creating the replicated graph for the race "White"
figure_a2_white_replication <-
  ggplot(mapping = aes(x = figure_a2_data_white$reason,
                       y = figure_a2_data_white$percent)) +
  geom_col() +
  theme_classic() +
  labs(x = "Impediment to voter ID", y = "Percentage") +
  scale_x_discrete(limits = c("ID-Capable", "Hardship", "Relocation")) +
  coord_flip() +
  # The geom_text function used to add the labels to the graph was obtained from
  # R Graphics Cookbook:
  # https://r-graphics.org/recipe-bar-graph-labels
  # The hjust argument used to align the labels was obtained from
  # Cédric Scherer's website:
  # https://www.cedricscherer.com/2021/07/05/a-quick-how-to-on-labelling-bar-graphs-in-ggplot2/
  geom_text(aes(label = figure_a2_data_white$label),
            hjust = c(1, 1, 1),
            colour = "orange") +
  ggtitle("White") +
  # The expand_limits function used to change the upper limit of the percent
  # axis's scale was obtained from the tidyverse ggplot2 website:
  # https://ggplot2.tidyverse.org/reference/expand_limits.html
  expand_limits(y = 45)

@@

# Creating the replicated graph for the race "Black"
figure_a2_black_replication <-
  ggplot(mapping = aes(x = figure_a2_data_black$reason,
                       y = figure_a2_data_black$percent)) +
  geom_col() +
  theme_classic() +
  labs(x = "Impediment to voter ID", y = "Percentage") +
  scale_x_discrete(limits = c("ID-Capable", "Hardship", "Relocation")) +
  coord_flip() +
  # The geom_text function used to add the labels to the graph was obtained from
  # R Graphics Cookbook:
  # https://r-graphics.org/recipe-bar-graph-labels
  # The hjust argument used to align the labels was obtained from
  # Cédric Scherer's website:
  # https://www.cedricscherer.com/2021/07/05/a-quick-how-to-on-labelling-bar-graphs-in-ggplot2/
  geom_text(aes(label = figure_a2_data_black$label),
            hjust = c(1, 1, 1),
            colour = "orange") +
  ggtitle("Black") +
  # The expand_limits function used to change the upper limit of the percent
  # axis's scale was obtained from the tidyverse ggplot2 website:
  # https://ggplot2.tidyverse.org/reference/expand_limits.html
  expand_limits(y = 45)

@@

# Creating the replicated graph for the race "Latinx"
figure_a2_latinx_replication <-
  ggplot(mapping = aes(x = figure_a2_data_latinx$reason,
                       y = figure_a2_data_latinx$percent)) +
  geom_col() +
  theme_classic() +
  labs(x = "Impediment to voter ID", y = "Percentage") +
  scale_x_discrete(limits = c("ID-Capable", "Hardship", "Relocation")) +
  coord_flip() +
  # The geom_text function used to add the labels to the graph was obtained from
  # R Graphics Cookbook:
  # https://r-graphics.org/recipe-bar-graph-labels
  # The hjust argument used to align the labels was obtained from
  # Cédric Scherer's website:
  # https://www.cedricscherer.com/2021/07/05/a-quick-how-to-on-labelling-bar-graphs-in-ggplot2/
  geom_text(aes(label = figure_a2_data_latinx$label),
            hjust = c(1, 1, 1),
            colour = "orange") +
  ggtitle("Latinx") +
  # The expand_limits function used to change the upper limit of the percent
  # axis's scale was obtained from the tidyverse ggplot2 website:
  # https://ggplot2.tidyverse.org/reference/expand_limits.html
  expand_limits(y = 45)

@@

@@

@@

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false

#### Loading Packages ####

# install.packages("tidyverse")
# install.packages("patchwork")
# install.packages("here")
library(tidyverse)
library(patchwork)
library(here)
```

```{r}
#| echo: false
#| warning: false
#| message: false

# Loading the cleaned data
reasons_data_cleaned <- read_csv(here::here("data/replication/reasons_data_cleaned.csv"))
```

@@

Using the R programming language (R Core Team 2023) and the tidyverse (Wickham et al. 2019), patchwork (Pedersen 2024), haven (Wickham, Miller, and Smith 2023), labelled (Larmarange 2023), and here (Müller 2020) packages, three figures from *Who Do Voter ID Laws Keep from Voting?* by Fraga and Miller (2022) were reproduced.

```{r}
#| echo: false
#| warning: false
#| label: fig-2
#| fig-cap: "Reproduction of Figure 2 from Fraga and Miller (2022)"

@@

# Creating the replicated graph
figure_2_replication <-
  ggplot(mapping = aes(x = reorder(figure_2_data$reason, figure_2_data$percent,
                                   decreasing = TRUE),
                       y = figure_2_data$percent)) +
  geom_col() +
  theme_classic() +
  labs(x = "Impediment to voter ID", y = "Percentage",
       title = "Figure 2. Impediments cited by Texas voters in 2016") +
  coord_flip() +
  # The geom_text function used to add the labels to the graph was obtained from
  # R Graphics Cookbook:
  # https://r-graphics.org/recipe-bar-graph-labels
  # The hjust argument used to align the labels was obtained from
  # Cédric Scherer's website:
  # https://www.cedricscherer.com/2021/07/05/a-quick-how-to-on-labelling-bar-graphs-in-ggplot2/
  geom_text(aes(label = figure_2_data$label),
            hjust = c(0, 0, 0, 0, 0, 0, 0, 0),
            colour = "red",
            size = 3) +
  # The expand_limits function used to change the upper limit of the percent
  # axis's scale was obtained from the tidyverse ggplot2 website:
  # https://ggplot2.tidyverse.org/reference/expand_limits.html
  expand_limits(y = 40)

@@

```{r}
#| echo: false
#| warning: false
#| label: fig-3
#| fig-cap: "Reproduction of Figure 3 from Fraga and Miller (2022)"

@@

# Creating the replicated graph
figure_3_replication <-
  ggplot(mapping = aes(x = reorder(figure_3_data$reason, figure_3_data$percent,
                                   decreasing = TRUE),
                       y = figure_3_data$percent)) +
  geom_col() +
  theme_classic() +
  labs(x = "Impediment to voter ID", y = "Percentage",
       title = "Figure 3. Binned impediments cited") +
  coord_flip() +
  # The geom_text function used to add the labels to the graph was obtained from
  # R Graphics Cookbook:
  # https://r-graphics.org/recipe-bar-graph-labels
  # The hjust argument used to align the labels was obtained from
  # Cédric Scherer's website:
  # https://www.cedricscherer.com/2021/07/05/a-quick-how-to-on-labelling-bar-graphs-in-ggplot2/
  geom_text(aes(label = figure_3_data$label),
            hjust = c(0, 0, 0),
            colour = "red",
            size = 3) +
  # The expand_limits function used to change the upper limit of the percent
  # axis's scale was obtained from the tidyverse ggplot2 website:
  # https://ggplot2.tidyverse.org/reference/expand_limits.html
  expand_limits(y = 40)

@@

\newpage

```{r}
#| echo: false
#| warning: false
#| label: fig-a2
#| fig-cap: "Reproduction of Figure A2 from Fraga and Miller (2022)"

@@

# Creating the replicated graph for the race "White"
figure_a2_white_replication <-
  ggplot(mapping = aes(x = figure_a2_data_white$reason,
                       y = figure_a2_data_white$percent)) +
  geom_col() +
  theme_classic() +
  labs(x = "Impediment to voter ID", y = "Percentage") +
  scale_x_discrete(limits = c("ID-Capable", "Hardship", "Relocation")) +
  coord_flip() +
  # The geom_text function used to add the labels to the graph was obtained from
  # R Graphics Cookbook:
  # https://r-graphics.org/recipe-bar-graph-labels
  # The hjust argument used to align the labels was obtained from
  # Cédric Scherer's website:
  # https://www.cedricscherer.com/2021/07/05/a-quick-how-to-on-labelling-bar-graphs-in-ggplot2/
  geom_text(aes(label = figure_a2_data_white$label),
            hjust = c(0, 0, 0),
            colour = "red",
            size = 2) +
  ggtitle("White") +
  # The expand_limits function used to change the upper limit of the percent
  # axis's scale was obtained from the tidyverse ggplot2 website:
  # https://ggplot2.tidyverse.org/reference/expand_limits.html
  expand_limits(y = 45)

@@

# Creating the replicated graph for the race "Black"
figure_a2_black_replication <-
  ggplot(mapping = aes(x = figure_a2_data_black$reason,
                       y = figure_a2_data_black$percent)) +
  geom_col() +
  theme_classic() +
  labs(x = "Impediment to voter ID", y = "Percentage") +
  scale_x_discrete(limits = c("ID-Capable", "Hardship", "Relocation")) +
  coord_flip() +
  # The geom_text function used to add the labels to the graph was obtained from
  # R Graphics Cookbook:
  # https://r-graphics.org/recipe-bar-graph-labels
  # The hjust argument used to align the labels was obtained from
  # Cédric Scherer's website:
  # https://www.cedricscherer.com/2021/07/05/a-quick-how-to-on-labelling-bar-graphs-in-ggplot2/
  geom_text(aes(label = figure_a2_data_black$label),
            hjust = c(0, 0, 0),
            colour = "red",
            size = 2) +
  ggtitle("Black") +
  # The expand_limits function used to change the upper limit of the percent
  # axis's scale was obtained from the tidyverse ggplot2 website:
  # https://ggplot2.tidyverse.org/reference/expand_limits.html
  expand_limits(y = 45)

@@

# Creating the replicated graph for the race "Latinx"
figure_a2_latinx_replication <-
  ggplot(mapping = aes(x = figure_a2_data_latinx$reason,
                       y = figure_a2_data_latinx$percent)) +
  geom_col() +
  theme_classic() +
  labs(x = "Impediment to voter ID", y = "Percentage") +
  scale_x_discrete(limits = c("ID-Capable", "Hardship", "Relocation")) +
  coord_flip() +
  # The geom_text function used to add the labels to the graph was obtained from
  # R Graphics Cookbook:
  # https://r-graphics.org/recipe-bar-graph-labels
  # The hjust argument used to align the labels was obtained from
  # Cédric Scherer's website:
  # https://www.cedricscherer.com/2021/07/05/a-quick-how-to-on-labelling-bar-graphs-in-ggplot2/
  geom_text(aes(label = figure_a2_data_latinx$label),
            hjust = c(0, 0, 0),
            colour = "red",
            size = 2) +
  ggtitle("Latinx") +
  # The expand_limits function used to change the upper limit of the percent
  # axis's scale was obtained from the tidyverse ggplot2 website:
  # https://ggplot2.tidyverse.org/reference/expand_limits.html
  expand_limits(y = 45)

@@

# Combining the axis labels on the combined graph
figure_a2_replication <- figure_a2_replication +
  plot_layout(axes = "collect")

@@

\newpage

@@

Alexander R. (2023). *Telling Stories with Data*. Boca Raton: CRC Press. <https://tellingstorieswithdata.com/>.

Fraga BL, Miller MG. (2022). "Who Do Voter ID Laws Keep from Voting?" *The Journal of Politics* 84 (2): 1091–1105. <https://doi.org/10.1086/716282>.

Larmarange J (2023). *labelled: Manipulating Labelled Data*. R package version 2.12.0, <https://CRAN.R-project.org/package=labelled>.

Müller K (2020). *here: A Simpler Way to Find Your Files*. R package version 1.0.1, <https://CRAN.R-project.org/package=here>.

Pedersen T (2024). *patchwork: The Composer of Plots*. R package version 1.2.0, <https://CRAN.R-project.org/package=patchwork>.

R Core Team (2023). *R: A Language and Environment for Statistical Computing*. R Foundation for Statistical Computing, Vienna, Austria. <https://www.R-project.org/>.

Wickham H, Averick M, Bryan J, Chang W, McGowan LD, François R, Grolemund G, Hayes A, Henry L, Hester J, Kuhn M, Pedersen TL, Miller E, Bache SM, Müller K, Ooms J, Robinson D, Seidel DP, Spinu V, Takahashi K, Vaughan D, Wilke C, Woo K, Yutani H (2019). “Welcome to the tidyverse.” *Journal of Open Source Software*, 4 (43), 1686. doi:10.21105/joss.01686 <https://doi.org/10.21105/joss.01686>.

Wickham H, Miller E, Smith D (2023). *haven: Import and Export 'SPSS', 'Stata' and 'SAS' Files*. R package version 2.5.4, <https://CRAN.R-project.org/package=haven>.
